Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-11 02_Paper/paper.tex
Conclusions and lessons learnt

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{Author name}

@@

While implementing ML models to QC, several challenges arise that have not yet been completely addressed, e.g., what to consider while evaluating the output from ML models for industrial applications? (model accuracy vs applicability at industrial environments); what steps should be followed to prepare the data for predictive QC methods?; and what findings and lessons are worth to consider for further applications in the area?. 
For this, we cover the methods used in quality check in production, as well as the bases of predictive analytics in production (Section.~\ref{sec:related_works}). 
We describe a suitable industrial platform to implement the ML models (Section.~\ref{sec:democell}).
Then, we explain the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
Finally, we describe the remarks and findings achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:conclusion}).

@@

\subsection{Lesson Learned} % 1/2 Page

\textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data within each other due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture. 
To overcome the situation stated above, it was necessary to reprogram big sections of the machine control system.

\textbf{Data synchronization}; two OPC-UA servers were used on this implementation. This lead to a series of data synchronization problems due to differences on the internal clock of both servers.
In order to solve the issue, it was needed to write a time-stamp synchronization script that was deployed during the data preprocessing phase. Without harmonious time-stamps, determining the production cycle would have been impossible and the input data for the ML model would have been useless, and the model inaccurate.

@@

\textbf{Adapting the industry 4.0 demonstration cell}; the initial state of the demonstrator was very limited. Even though the process was well known, the lack of labels or flags whenever certain actions occurs, made complicated to have accurate data sampling from each assembly cycle. In order to overcome this uncertainty, we modify the machine program to raise specify flags whenever certain actions would be executed.

@@

\section*{Acknowledgments}
This work was funded by the European Regional Development Fund (ERDF) with the project name "ManuBrain"

>>>>

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{Peter Burggräf et al.}

@@

While implementing ML models to QC, several challenges arise that have not yet been completely addressed, e.g., what to consider while evaluating the output from ML models for industrial applications? (model accuracy vs applicability at industrial environments); what steps should be followed to prepare the data for predictive QC methods?; and what findings and lessons are worth to consider for further applications in the area?. 
For this, we cover the methods used in quality check in production, as well as the bases of predictive analytics in production (Section.~\ref{sec:related_works}). 
We describe a suitable industrial platform to implement the ML models (Section.~\ref{sec:democell}).
Then, we explain the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
Finally, we describe the remarks and findings achieved after the finalization of this project phase (Section.~\ref{sec:conclusion}), as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:lessons}).

@@

\section{Lesson Learned} \label{sec:lessons} % 1/2 Page

\textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture. 
To overcome the situation stated above, it was necessary to reprogram big sections of the machine control system.

\textbf{Data synchronization}; two OPC-UA servers were used on this implementation. This lead to a series of data synchronization problems due to differences in the internal clock of both servers.
To solve the issue, it was needed to write a time-stamp synchronization script that was deployed during the data preprocessing phase. Without harmonious time-stamps, determining the production cycle would have been impossible and the input data for the ML model would have been useless, and the model inaccurate.

@@

\textbf{Adapting the industry 4.0 demonstration cell}; the initial state of the demonstrator was very limited. Even though the process was well known, the lack of labels or flags whenever certain actions occur, made it complicated to have accurate data sampling from each assembly cycle. To overcome this uncertainty, we modified the machine program to raise specific flags whenever certain actions were executed.

@@

\section*{Acknowledgments}
This work was funded by the European Regional Development Fund (ERDF) within the project "ManuBrain".
